The robot who pretend-played with me

### 2017-04-06 paper.tex
Parten's stages of play

>>>>

\subsection{Stages of play}

In developmental psychology, Parten's {\bf stages of
play}~\cite{parten1932social}:

\begin{enumerate}
    \item {\bf Solitary (independent) play}: Playing separately from
        others, with no reference to what others are doing.
    \item {\bf Onlooker play}: Watching others play. May engage in
        conversation but not engaged in doing. True focus on the children at
        play.
    \item {\bf Parallel play} (adjacent play, social coaction): Playing
        with similar objects, clearly beside others but not with them (near
        but not with others.)
    \item {\bf Associative play}:  Playing with others without
        organization of play activity. Initiating or responding to
        interaction with peers. 
    \item {\bf Cooperative play}: Coordinating one’s behavior with that
        of a peer. Everyone has a role, with the emergence of a sense of
        belonging to a group. Beginning of "team work."
\end{enumerate}
